
\documentclass[overlapped,line,letterpaper]{res}

\usepackage{ifpdf}

\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi



%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

%---------------------------------------------------------------------------

\name{James A. Stickney}

\begin{resume}

\begin{ncolumn}{2}

41 Pleasant Steet & Phone:  (774) 253-1786 \\
Wakefield               & Email: {\tt jim.stickney@gmail.com} \\
Massachusetts 01880, USA
\end{ncolumn}


%---------------------------------------------------------------------------

\section{\bf Summary}

 {\bf Accomplished experienced researcher} in atomic physics, focusing on applications using atoms including gyroscopes and accelerometers.  Trained as a theoretical physicist and has spend the past six years supporting an experimental group.

Published 11 (7 as first author) peer-reviewed articles and given presentations at professional meetings.


 {\bf Computer Skills:} Experienced in computational modeling, including parallel programing (MPI), graphical user interfaces, and 3D visualizations of complex data (VTK).  Experience in developing embedded systems for control systems.  
Programing Languages: Matlab, Python, Fortran, C, C++, and CUDA.

Expertise using \LaTeX, Emacs, Linux, and Microsoft products. 


 {\bf Management Skills:} Principal investigator on a \$4.8M Research and Development contract for Utah State University and the Air Force
 Research Laboratory at Hanscom AFB.



%---------------------------------------------------------------------------
\section{\bf Present Position}

\begin{format}
\title{l}\dates{r}\\
\employer{l}\location{r}\\
\body\\
\end{format}



\title{Physicist}
\employer{Stuart Radiance Laboratory}
\location{Bedford, MA}
\dates{2011-present}

\begin{position}
supervisor: Chad Fish \hfill (435) 713-3355
 \end{position}



\section{\bf Research Experience}

 {\bf Theory:} Expert at modeling complex systems both analytically and numerically.  
Extensive experience analyzing nonlinear phenomena including: quantum optics, Bose Einstein condensation, and non-equilibrium statistical mechanics.  

Strong numerical modeler with experience including: nonlinear systems, optimizations, Monte-Carlo solvers, finite element analysis, three dimensional visualizations, GUI interfaces, and electromagnetic fields.  Worked with high performance computing using MPI and GPGPU programming using CUDA. 

 {\bf Experiment:} Experience with ultra-high vacuum, optical systems, building control electronics using embedded systems, data collection,  and data analysis.  

Capable machinist including programing and using CNC machines.


%---------------------------------------------------------------------------

\section{\bf Education}
Ph.D. Physics, Worcester Polytechnic Institute, May 2008 \\
Dissertation: A theoretical analysis of Bose-Einstein condensate based beamsplitters, interferometers, and transistors \\
Advisor: Alex Zozulya \hfill (508)831-5254

M.S. Physics, Worcester Polytechnic Institute, 2003

%---------------------------------------------------------------------------


\end{resume}

\end{document}


\section{\bf Research Experience}

\begin{format}
\title{l}\dates{r}\\
\employer{l}\location{r}\\
\body\\
\end{format}



\title{Physicist}
\employer{United States Air Force}
\location{Hanscom AFB, MA}
\dates{2007-present}

\begin{position}
Theoretical and experimental work on atom interferometry for inertial navigation systems at the Air Force Research
Laboratory.  Continued development of cold atom modeling tool.  Developed a new process for building atom chips using direct bonded copper substrates.  Analyzed the
optimal shape of wires used on atom chips.  
 \end{position}



\title{Research Scientist}
\employer{Space Dynamics Laboratory}
\location{North Logan, UT}
\dates{2007-2009}
\begin{position}
 Theoretical and experimental work on atom interferometry for inertial navigation systems.  Introduced a new type of
 interferometer design for use in rotation sensing and analyzed the performance limits of this sensor.  Developed a new
 type of atom trap that produce a very harmonic potential.  This type of trap will be necessary for the realization
 of a trapped atom interferometer.  Wrote a cold atom modeling tool to speed the development of cold atom based
 sensors.  This tool contains a trap optimizer and a Monte-Carlo solver for calculating the temperature, density,
 location, and number of trapped atoms.   Since 2009, principal investigator on a \$4.8M Research and Development contract for Utah State University and the Air Force
 Research Laboratory at Hanscom AFB.
\end{position}


\title{Graduate Research Assistant}
\employer{Alex A. Zozulya}
\location{Worcester Polytechnic Institute}
\dates{2001-2007}
\begin{position}
 Theoretical work on Bose Einstein condensate(BEC) based devices.  The operation of BEC based interferometers that use a double well potential was
 extensively analyzed.  A recombination instability for this type of interferometer was predicted.  A simple BEC
 transistor was proposed that uses a triple well potential.  Analysis of BEC based interferometers that use optical
 pulses to manipulate the atoms was preformed.  A very simple way to understand why this type of interferometer loses
 its coherence was presented as well as methods for increasing the coherence.  
\end{position}


\title{Undergraduate Research Assistant}
\employer{Grover A Swartzlander}
\location{Worcester Polytechnic Institute}
\dates{1998-2000}
\begin{position}
  Experimental work building optical tweezers for trapping and manipulation micron sized objects. 
\end{position}









\section{\bf Peer-Reviewed Scientific Publications}

[1] ``Expansion of a {B}ose-{E}instein condensate from a micro trap into a waveguide,'' J. A. Stickney and A.A. Zozulya,
 Phys. Rev. A. \textbf{65}, 053612 (2002).

[2] ``Wave-function recombination instability in cold-atom interferometers,'' J. A. Stickney and A. A. Zozulya,
Phys. Rev. A. \textbf{66}, 053601 (2002).

[3] ``Influence of nonadiabaticity and nonlinearity on the operation of cold-atom beam splitters,'' J. A. Stickney and A. A. Zozulya,
Phys. Rev. A. \textbf{68}, 013611 (2003).

[4] ``Decrease in the visibility of the interference fringes in a cold-atom accelerometer,'' J. A. Stickney and A. A. Zozulya,
Phys. Rev. A. \textbf{69}, 063611 (2004).

[5] ``Transistor like behavior of a {B}ose-{E}instein condensate in a triple-well potential,'' J. A. Stickney, D. Z. Anderson, and A. A. Zozulya,
Phys. Rev. A. \textbf{75}, 013608 (2007).

[6] ``Increasing the coherence time of {B}ose-{E}instein-condensate interferometers with optical control of dynamics,'' J. A. Stickney, D. Z. Anderson, and A. A. Zozulya, Phys. Rev. A \textbf{75}, 063603 (2007).

[7] ``MATLAB codes for teaching quantum physics: Part 1,'' R. Garcia, A. Zozulya, J. Stickney, arXiv:0704.1622 (2007).

[8] ``Theoretical analysis of a single- and double-reflection atom interferometer in a weakly confining magnetic trap,''
J. A. Stickney, R. P. Kafle, D. Z. Anderson, and A. A. Zozulya, Phys. Rev. A \textbf{77}, 043604 (2008).

[9] ``Collisional decoherence in trapped-atom interferometers that use nondegenerate sources,'' J. A. Stickney,
M. B. Squires, J. Scoville, P. Baker, and S. Miller, Phys. Rev. A \textbf{79}, 013618 (2009).

[10] ``Adjustable microchip ring trap for cold atoms and molecules,''
P.M. Baker, J.A. Stickney, M.B. Squires, J.A. Scoville, E.J. Carlson, W.R. Buchwald, S.M. Miller,
Phys. Rev. A. \textbf{80}, 063615 (2009).

[11] ``Atom chips on direct bonded copper substrates,'' Matthew B. Squires, James A. Stickney, Evan J. Carlson, Paul M. Baker, Walter R. Buchwald, Sandra Wentzell, and Steven M. Miller
arXiv:1007.4851. (In press at RSI)

%[11] ``Atom chips on direct bonded copper substrates,'' M.B. Squires, J.A. Stickney, E.J. Carlson, P.M. Baker,
%W.R. Buchwald, S.M. Miller,         
%------------------------------------------------------------------------------

\section{\bf Selected Posters and Presentations}

[1] ``Transistor like behavior of a Bose Einstein condensate in triple well potential,'' March Meeting of the American Physics Society, Baltimore, MD, March 2006.

[2] ``BEC transistor,'' DAMOP Meeting 2006, Knoxville, TN, May 2006.

[3] ``Analysis of the coherence time of a Bose-Einstein-condensate interferometer with optical control of dynamics,''
March Meeting of the American Physics Society, Denver, CO, March 2007.

[4] ``Atomoptics and Atomtronics'' Physics Colloquia, WPI, Worcester MA, April 2007.

[5] ``Theoretical analysis of trapped atom interferometers using laser cooled sources,'' International Conference on
Atomic Physics, Storrs, CT, July 2008.

[5] ``Collisional decoherence in trapped atom interferometers that use non-degenerate sources,'' gBECi Review, Las
Vegas, NV, December 2009.


%---------------------------------------------------------------------------



%---------------------------------------------------------------------------


\section{\bf Service}

\begin{itemize}
\item President, Graduate Physics Student Society, 2003-2005
\item  ``Machine shop guru'', WPI physics Department 2001-2007
\item Organizer of the graduate student seminar series, 2006-2007
\end{itemize}

%%---------------------------------------------------------------------------%%

\section{\bf Honors and Awards}
\begin{itemize}
\item MQP (undergraduate thesis): Award for best undergraduate research award May, 2001
\item Second Place: Best poster presentation,  WPI Graduate Research Achievement Day, March 2007
\item Member of $\Sigma \Xi$
\item Memeber of SPS
\item Member of $\Sigma \Pi \Sigma$ Physics student honor society
\end{itemize}

%%---------------------------------------------------------------------------%%


\section{\bf References}

\noindent
Steven Miller \\
Senior Physicist AFRL/RVBYM, \\
29 Randolph Rd. Hanscom AFB, MA 01731-3010.  \\
TEL: (781) 377-2807.  FAX: (781) 377-8900.  EMAIL: steven.miller@hanscom.af.mil.

\noindent
Alex A. Zozulya \\
Department of Physics, Worcester Polytechnic Institute, \\
100 Institute Rd., 213C Olin Hall, Worcester, MA 01609.  \\
TEL: (508)831-5254.  FAX: 508/831-5886.  EMAIL: zozulya@wpi.edu.

\noindent
Patricia H. Doherty \\
Institute for Scientific Research, Boston College\\
140 Commonwealth Avenue. Chestnut Hill, MA 02467 \\
TEL: (671) 552-8767.  FAX: (617) 552-2818.  EMAIL: Patrica.Doherty@bc.edu


 


\end{resume}

\end{document}

%%===========================================================================%%
